\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{lipsum}
\usepackage{setspace}
\name{Dan}{Shu}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{Highspeed IO Validation Engineer}\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +1 4082198739 & \enspace \color{blue} \href{mailto:dshu178@gmail.com}{dshu178@gmail.com} & \faHome\enspace San Jose, CA, USA \\
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/danshu/}{in/danshu} &
\faGithub\enspace \color{blue} \href{https://danzhoushu.github.io/}{danzhoushu.github.io/}
\end{tabular}
\end{center}

\section{Profile}
{10+ years of silicon industry experience building up capability and capacity focusing on delivering results. True innovator with strong industry connections. A passionate linchpin who can quickly connect dots and identify new opportunities.}

\section{Areas of Expertise}
{Highspeed IO - SerDes - IEEE802.3 Ethernet - PCIe - Optical QSFP/OSFP - OpenZR/ZR+ - OIF - Chiplet - UCIe - BoW - CXL - RF/mmW - IEEE802.11 WiFi - BT - UWB - 5G NRU - Link Budget - RF Front End - Low power - SI/PI/EM simulation - Instrument - ATE - Data Science- Database - Machine Learning}

\section{Professional Experience}
\customcventry{07/2023 ‐ present}{{\color{blue}\href{https://danzhoushu.github.io/year-archive/}{(Freelance/Consultant)}}}{HighSpeed IO, RF/mmW Architect,}{San Jose, CA}{}{}{}{
{\begin{itemize}[leftmargin=0.6cm, itemsep=0pt, label={\textbullet}]
\item Providing consultancy services for chiplet startup company on highspeed I/O.
\item Working with RF and Si/Pi expertise on SerDes/optical link budget analysis.
\item Increasing I/O throughput by decreasing RF path loss and using high order modulations.
\item Offering RF architect consultancy services to Front-End-Module companies. 
\end{itemize}}}


\customcventry{04/2023 ‐ 06/2023}{{\color{blue}\href{https://www.macom.com/}{(Macom)}}}{Principal Application Engineer}{Santa Clara, CA}{}{}{}{
{\begin{itemize}[leftmargin=0.6cm, itemsep=0pt, label={\textbullet}]
\item Validated 8 x 112Gbaud PAM4/Coherent TIA and Laser driver.
\item Invented 112Gbaud PAM4/Coherent TIA process, voltage, temperature (PVT) characterization/validation method using machine learning algorithm.
\item Led the team to visualize the large validation dataset (100k .S4P files).
\end{itemize}}}

\customcventry{10/2014 ‐ 03/2023}{{\color{blue}\href{https://www.qualcomm.com/}{(Qualcomm Atheros)}}}{SENIOR STAFF, HWS Architect}{Santa Clara, CA}{}{}{}{
{\begin{itemize}[leftmargin=0.6cm, itemsep=0pt,label={\textbullet}]
\item Led the team to finish RF Front End (RFFE) design validation activities.
    \begin{itemize}[itemsep=0pt]
    \item Hands-on validated, characterized FEMs for EVM, drooping, Mask, ACP, IIP2/3, NF, power efficiency etc. over process, voltage, and temperature. 
    \item Conducted line-up simulation analysis over multi-stage Tx/Rx look up tables. Validated simulation results on reference design.
    \item Successfully simulated, predicted, and validated WiFi7 MLO 5/6G bands co-exist mode Lo spur 2nd order mixer effects caused Rx desense.
    \item Worked on validating of linear/nonlinear/Doherty PA with DPD, memory DPD, CFR, ET, APT, multi modes PA/LNA for low power FEM designs. 
    \end{itemize}
\item Partner with Qualcomm’s different technology teams to validate cutting edge design innovative digital enhancement features to wireless products.
    \begin{itemize}[itemsep=0pt]
    \item Validated 11be/WiFi7 CFR waveforms from SoC system to RF front end for compensating various RF impairments.
    \end{itemize}
\item Invented mobile SoC dynamic voltage control algorithm for power saving and throughput improvement based on multivariate machine learning models.
    \begin{itemize}[itemsep=0pt]
    \item Hands-on collected data in the lab over 1000+ user cases using DoE approach for design wins at major customer’s mobile design.
    \item Used multivariate machine learning models to calculate the polynomial functions SoC Vmin vs. SoC Process, Tj, and Throughput.
    \end{itemize}
\item Worked on validating 4 categories of battery driven mobile system-level low power design.
    \begin{itemize}[itemsep=0pt]
    \item Implemented process, voltage, Tj (PVT) vs. throughput relationship validation.
    \item Validated the SoC circuit timing design such as power collapse, clock gate etc.
    \item Validated low power features per Day-of-Use (DoU) cases.
    \item Helped CSMA/CA based low power design approach validation.
    \end{itemize}    
\item Maintained the pace of per year learning/creating 2 new things..
    \begin{itemize}[itemsep=0pt]
    \item 2023, Built MSSQL database and implemented off-the-shelf DPD solution.
    \item 2022, Invented FEM drooping characterization method.
    \item 2021, Invented SoC supply dynamic voltage setting method. 
    \item 2020, Built low power and thermal characterization tester.
    \item 2019-18, Built wifi6e/7 FEM validation and characterization tester.
    \item 2017 and before, led and finished the 11be FTM design validation tester (DVT) solutions and started mission mode performance vs. power validation efforts. 
    \end{itemize}    
\end{itemize}}}

\customcventry{03/2013 ‐ 09/2014}{{\color{blue}\href{https://www.broadcom.com/}{(Broadcom)}}}{PRINCIPAL ENGINEER, ATE Architect}{Santa Clara}{}{}{
{\begin{itemize}[leftmargin=0.6cm, itemsep=0pt, label={\textbullet}]
\item Solved 10G, 25G Serdes ATE load board PCB design challenges for 144 lanes switch SoC.  
\item Published data analysis paper “Quantifying Shmoo Results: Brain Storm”.
\end{itemize}}}

\customcventry{11/2011 ‐ 9/2012}{{\color{blue}\href{https://www.amd.com/en.html}{(AMD Canada)}}}{I/O Consultant}{Markham, ON, Canada}{}{
{\begin{itemize}[leftmargin=0.6cm, itemsep=0pt, label={\textbullet}]
\item Solved PCIE Gen3(8G/s) and GDDR5 ATE test challenges for GPU/APU.
\end{itemize}}}

\customcventry{05/2004 ‐ 11/2011}{{\color{blue}\href{https://www.semtech.com/}{(Semtech/Gennum)}}}{Principal Engineer}{Burlington, ON, Canada}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Led a task force to deliver the 1st generation Thunderbolt cable drivers (CDRs and EQs) project for the Apple Mac Computer.
\item Simulated TIA oscillation issue by HFSS and provided GSG idea to boost TIA gain from 3kohm to 60kohm.
\item Built 26.5GHz BW optical domain characterization and validation lab.
\end{itemize}}}

\section{Education}
\customcventry{}{\color{blue}\href{http://en.xjtu.edu.cn/}{Xi'an Jiaotong University}}{Bachelor degree in Electronic Engineering}{Xi'an, China}{}{}
\customcventry{}{\color{blue}\href{https://en.uestc.edu.cn/}{University of Electronic Science and Technology of China}}{Post graduate studies, on-leave}{Chengdu, China}{}{}

\section{Online Courses \& Certifications}
{\begin{itemize}[label=\textbullet, itemsep=0pt]
      \item JAVA (2022)
      \item Regression Models, Johns Hopkins online (2015) - \underline{\color{blue}\href{https://www.coursera.org/account/accomplishments/certificate/678GCXVGHW}{Coursera}}
      \item Statistical Inference, Johns Hopkins online (2015) - \underline{\color{blue}\href{https://www.coursera.org/account/accomplishments/certificate/4MAV4C4QVK/}{Coursera}}
      \item Machine Learning, Stanford online  (2014) - \underline{\color{blue}\href{https://github.com/dshu178/Certifications/blob/main/DanShu_Coursera_ml_2014.pdf}{Coursera}}
    \item Introduction To Databases, Stanford online (2013) - \underline{\color{blue}\href{https://github.com/danzhoushu/danzhoushu.github.io/blob/master/files/dshu178-98279-db--Winter2013-accomplishment.pdf}{Coursera}}
  \end{itemize}} 


\section{Skills}
{\begin{itemize}[label=\textbullet, itemsep=0pt]
\item {\textbf{Data Visualization:} Spotfile, JMP, Microsoft Power BI, Excel}
\item {\textbf{Simulation Software:} Matlab, SystemVue, ADS, HFSS}
\item {\textbf{Standards} IEEE802.11, IEEE802.3, BT, PCIe, UCIe, BoW, CXL, Ethernet COM}
\item {\textbf{Program languages:} Python, C++, JAVA, SQL, Linux scripts}
\item {\textbf{Instruments:} VNA, VGA, VSA, AWG, BERT, Real/Sampler Scope, LCA, LCR meter, current profile, source meter, Optical tester, ATE V93K}
\end{itemize}}

\end{document}